%!TEX TS-program = xelatex
\documentclass[]{thoma-cv}
\usepackage{chronosys}
\begin{document}
\header{stephen}{thoma}
       {full stack developer}


% newlines force line breaks in aside
\begin{aside}
  \section{about}
    4170 Monroe Dr.
    Unit C. 80303
    Boulder, Colorado
    ~
    \href{mailto:stephen@stephenthoma.com}{stephen@}
    \href{http://stephenthoma.com}{stephenthoma.com}
    \href{https://github.com/sthoma}{github://sthoma}
  \section{programming}
    {\color{red} $\varheartsuit$} Java, C
    Javascript
    {\fontsize{8}{9.6} \selectfont \{Angular, Node.js\}}
    CSS3, HTML5
    Python \& Scala
\end{aside}

\section{interests}
I am a Computer Science student mainly interested in machine learning,
natural language processing, data visualization, and human-computer interaction.
I am also very interested in sustainability, specifically Life Cycle Assessment.
When not programming, I enjoy rock climbing, photography, and road cycling.

\section{education}

\startchronology
[startyear=2005, height=0.95pc, dates=false, color=gray]
\chronoperiode[color=red]{2007}{2012}{Fayetteville High School}
\chronoperiode[color=blue]{2012}{2014}{University of Colorado}
\chronoevent[markdepth=-25pt, date=false]{2010}{National Honor Society}
\chronoevent[markdepth=-43pt, date=false]{2011}{Rotary Scholar}
\chronoevent[markdepth=-30pt, date=false]{2013}{Wilderness First Responder}
\stopchronology

\begin{entrylist}
  \entry
    {since 2012}
    {Undergraduate degree {\normalfont in Computer Science}}
    {University of Colorado: Boulder}
    {Emphasis on \emph{Human Computer Interaction}}
  \entry
    {2008–2012}
    {Fayetteville High School}
    {}
    {GPA: 3.9}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {2014 - Pres.}
    {DevCoded Marketplace}
    {Sideproject.}
    {A marketplace for developers of video game enhancements to be paired       with clients to create custom game plugins.}
  \entry
    {2013-Pres.}
    {Airworx Cinema}
    {}
    {\emph{Cable-camera aerial cinematography and event photography.}}
  \entry
    {05-08 2014}
    {Access Fund Internship}
    {Summer Internship.}
    {Geo-location and data analysis / visualization of data regarding
    climbing areas.}
  \entry
    {07–08 2013}
    {Dairy Allocation Calculator}
    {Summer job.}
    {\emph{Creation of an easy method of allocation calculations to be used by dairy farmers.}}
  \entry
    {07–08 2010}
    {Research Internship.}
    {University of Arkansas}
    {\emph{Modelling the impact of the Deepwater Horizon oil spill on gulf coast ecosystem services.}}
  \entry{02 2009}{Regional Ricoh Sustainable Development Award}{}{}
  \entry
    {02–07 2009}
    {LIP6/CNRS, Paris}
    {Research Internship.}
    {\emph{Visualization of complex networks.}}
\end{entrylist}

%\section{applications}

\end{document}
